Validated Model Counting Data \\ Version of \today

### 2023-02-21 doc/mc-data.tex
New information about weighted counts

>>>>

\section*{Computing Counts and Weighted Counts}

\begin{itemize}
\item Implemented package to represent numbers of form $a \cdot 2^b \cdot 5^c$.
  \begin{itemize}
  \item For unweighted counts, first compute density and then scale by $2^n$
  \item For unweighted counts, perform exact decimal arithmetic
  \item The set of numbers of this form is not closed under a reciprocal operation, but the weights in the competion are either of the form
    $w(x) + w(\overline{x}) = 1.0$ or $w(x) = w(\overline{x}) = 1$.  The latter case sums to 2, with reciprocal $1/2$.
  \end{itemize}
\item Can implement having $a$ be integer of arbitrary size and $b$ and $c$ being 32-bit integers.
\item Weighted counts ranged up to 260,909 digits.
\end{itemize}
